Untitled

### 2019-05-28 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

**Fig. 1** - Map showing all data used in the anlysis, coded by variable.
![Distribution of carbon data](https://github.com/forc-db/Global_Productivity/blob/master/results/figures/final_figures/maps/distribution_all_variables.png)

@@

\begin{table}
\centering
\caption{}
\label{table-paramvalues}
\begin{tabular}{ p{4cm} p{4cm} p{4cm} }
\hline \\ [-1.5ex]
Database &amp; Variables downloaded &amp; Citation \\ [1ex]
\hline \\ [-1.5ex]
WorldClim & mean annual temperature; temperature seasonality; annual temperature range; mean annual precipitation & [@Hijmans2005] \\ [1ex]
WorldClim2 & Vapour pressure; solar radiation & [@Fick2017] \\ [1ex]
Climate Research Unit (CRU) time-series dataset v 4.03 & Cloud cover; annual frost days; annual wet days; potential evapotranspiration & [@Harris2014] \\ [1ex]
Global Aridity Index and Potential Evapotranspiration Climate Database & Aridity; potential evapotranspiration & [@Trabucco2018] \\ [1ex]
TerraClimate & Vapour pressure deficit & [@Abatzoglou2018] \\ [1ex]
\hline
\end{tabular}
\end{table}

>>>>

---
output:
  pdf_document:
    fig_caption: yes
---

![Figure 1: Map showing all data used in the anlysis, coded by variable \label{figurelabel}](distribution_all_variables.png)

@@
